Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-09-11 ms/ms08_figures_boxenplot.tex
MS

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/eqtl_effect_boxenplot.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/gwas_effect_boxenplot.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/eqtl_signif_boxenplot.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/gwas_signif_boxenplot.png}
    \end{subfigure}

    \centering
    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_allele_freq.py/eur_af_boxenplot.png}
    \end{subfigure}
    %
    % Fig 9: eQTL gene distance
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_etissue_y_egene.py/boxenplot.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_egene_y_etissue.py/boxenplot.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_remapnr.py/boxenplot.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}

>>>>

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/eqtl_effect_ms_boxenplot.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/gwas_effect_ms_boxenplot.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/eqtl_signif_ms_boxenplot.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_gwas_count_y_beta_neglog10pval.py/gwas_signif_ms_boxenplot.png}
    \end{subfigure}

    \centering
    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_allele_freq.py/eur_af_boxenplot.png}
    \end{subfigure}
    %
    % Fig 9: eQTL gene distance
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/boxenplot_ms_closest_distance.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_etissue_y_egene.py/histplot.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_egene_y_etissue.py/histplot.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_remapnr.py/boxenplot_ms.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}
